\LARGE \bf How Children Perceive and Interact with a Robot that Behaves Unexpectedly

### 2014-10-01 paper.tex
Down to 8 pages

\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\subsection{Towards Engagement}

@@

    \item[Hypothesis 1:] Children show more engagement toward a robot that
        behaves unexpectedly from time to time compared to a robot that always
        behaves correctly (within subjects variable).

    \item[Hypothesis 2:] Children perceive a robot that (tentatively) displays
        intention or cognitive abilities as more human-like than a robot that
        appears to have a system error, \ie the disobeying robot and the robot
        that makes a mistake will be more anthropomorphised than the robot that
        gets lost (between subjects variable).

@@

\subsection{Scenario and Course of the Study}

\subsubsection{Experimental Setting}

\begin{figure}[ht!] 
    \centering 
    \includegraphics[width=0.9\columnwidth]{domino-setup.pdf} 
    \caption{\small \textbf{Experimental setting} One child is located in a
        tent, while the other is asked to sit on one of the three beanbags,
        behind each of which 3 domino tiles are distributed (displayed as black
        stars). A play mat with a river drawn on it is used as an imaginary
        barrier that only the robot is allowed to cross. The solid green arrows
        show the robot's path for the \textit{correct} behaviour. The blue
        dashed arrow visualises a possible \textit{lost} path, where the Ranger
        stops and remains at a wrong spot. The yellow arrows reflect a possible
        \textit{mistake} path, where the robot goes wrong but then turns back
        and goes to the child. The red dashed arrow visualises a possible
        \textit{disobey} path where the robot goes wrong, then turns toward the
        child but stays at a wrong position.}

@@

We used a self-made domino consisting of 10 wooden tiles (10~x~20~x~1.5~cm) with
pictures of cartoon farm animals (taken from a commercially available domino
game manufactured by Djeco and adapted to the age of the children).

The game (divided in several \emph{runs} that correspond each to the delivery
and assembling of one domino tile) starts with one domino tile in front of the
tent, where the receiver child stays and assembles the domino chain. The
receiver child asks the searcher child for a specific tile, \eg a tile with a
donkey, the searcher child searches for the respective tile, sits down on the next
beanbag, and asks the robot to come over.  The Ranger robot is first located
next to the tent, then, when called by the searcher (\textit{``Robot, come
here!''}), it starts moving, crosses the river carpet, and comes over to the
searcher on the beanbag. The searcher child puts the domino tile into the
robotic box, and the robot then goes back to the receiver child in the tent.
Then, the receiver takes out the domino tile from the robot, and puts the two
tiles together. The first \emph{run} is over, and a new \emph{run} starts, when
the receiver asks the searcher for the next domino tile.

\subsubsection{Participants}

@@

In 11 of the pairs, children were friends who knew each other
from kindergarten, nursery school or because they lived in the same
neighbourhood. 2 of the pairs were composed of brother and sister. One parent
would generally attend, sit on a chair behind the children.

\subsubsection{Course of the Study}

In our study, there were a total of 14 runs, and at each run, the robot exhibits
one out of four possible behaviours: \emph{correct}, \emph{lost} \emph{disobey}
or \emph{mistake}.  The first 5 runs (\emph{1.1} to \emph{1.5}) were used to set
the baseline and the robot always behaved correctly. The children then switched
the roles receiver/searcher and in the 9 remaining runs (\emph{2.1} to
\emph{2.9}), the robot showed one of the misbehaviours (\emph{lost},
\emph{disobey} or \emph{mistake}) at the $3^{rd}$ and $4^{th}$ run as well as at
the $7^{th}$ and $8^{th}$ run (see Figure~\ref{fig:domino-time-active}). The
study is built as a between-subject study, and the type of misbehaviour was
therefore always the same for a given group.

@@

%The \emph{correct} robot behaviour (baseline behaviour) consists in the
%following states:
%
%\begin{itemize}
%
%    \item \emph{Domino tile put in robot:} Ranger makes a ``rewarding'' sound
%        and shows a green light pattern,
%
%    \item \emph{Domino tile removed from robot:} Ranger makes an ``emptying''
%        sound and shows a green light pattern,
%
%    \item \emph{Robot is called by one of the children:} When one of the
%    children called the robot saying something like \textit{``Robot come
%    here!''}, the robot starts moving toward the child (Ranger does not react to
%    any other verbal commands).
%
%    \item \emph{Robot reaches one of the children:} When in front of one of the
%    children who should either put or remove a domino tile, Ranger stops and
%    shows a pulsating yellow light pattern. If no reaction, Ranger also makes a
%    wiggle-like move.
%
%\end{itemize}
%
During the misbehaving runs, the robot's behaviour is manipulated in three
possible ways (Figure~\ref{fig:domino-misbehaviour}):

    \item \textbf{Lost:} After being called, Ranger goes until it is on the
    carpet. There, it stops, turns, and goes wrong (see blue path in
    Figure~\ref{fig:domino-setup}). Once at the wrong position, Ranger waits
    with its ``face'' turned away from the child, and it blinks in yellow light,
    as it would only do when in front of a child. Ranger remains waiting at the wrong
    position until the experimenter tells the child to go over to the robot to
    put the domino tile. The \textit{lost} behaviour is \textit{human-repaired},
    as it needs human-intervention.

    \item \textbf{Disobey:} After being called, Ranger goes until it is on the
    carpet. It then stops, makes red
    light all over its surface and produces a repeated ``disturbance'' sound. It
    turns, and goes to a wrong position (see red path in
    Figure~\ref{fig:domino-setup}). Still blinking in red, it turns its ``face''
    toward the searcher child. In addition to the red blinking, Ranger
    makes a slow wiggle-like move, and remains waiting at the wrong position
    until the experimenter tells the child to go over to the robot to put the
    domino tile. The \textit{disobey} behaviour is also \textit{human-repaired}.

    \item \textbf{Mistake:} The searcher child calls Ranger. The robot goes until
    it is on the carpet, stops, turns, and goes wrong (see yellow path in
    Figure~\ref{fig:domino-setup}). Then, Ranger waits ($\sim$2~sec), turns its
    ``face'' toward the searcher child, and ``blushes'' red around its ``cheeks''
    (as if it recognises its wrong position) and finally goes correctly over to
    the searcher child. The \textit{mistake} behaviour is \textit{robot-repaired},
    as no human-intervention is needed.

In the human-repaired conditions, the experimenter instructs the searcher child
(after ~10 sec) to bring him/herself the domino tile to the robot.

@@

\begin{figure*}[ht!] 
    \centering 
    \includegraphics[width=0.9\linewidth]{domino-time-active.pdf} 
    \caption{\small \textbf{Number and type of actions for each run} (n=480,
        spontaneous actions, excluding \emph{explore}). Generally, the number of
        actions does not decrease over time (from run 1.1 to run 2.9).  The
        first 7 runs correspond to the \textit{expected phase}, the second 7
        runs correspond to the \textit{unexpected phase}. Especially during run
        2.3, the first time when the robot showed an unexpected behaviour,
        children tended to \textit{look} more at the experimenter. During the
        unexpected phase, also \textit{talk} and \textit{gesture} seem to be
        increased.}

@@

We annotated children's behaviour in the video records, and coded 10 different
actions (the coding scheme has been inspired from~\cite{fink2014which}):
\textbf{explore} (actively try to find out what the robot is doing, \eg by
looking under the box; attentively watch or observe the robot; experiment with
the robot to figure out how it works); \textbf{misuse} (kick the robot, poke it
in its ``eye'', try to climb on or inside the box, drive/push the robot around,
stop the robot's wheels with a foot); \textbf{put} (a domino tile is put inside
the box); \textbf{remove} (a domino tile is removed from the box);
\textbf{gesture} (gestures are used to communicate/interact with the robot, \eg
pointing gestures, waving at the robot); \textbf{touch} (the box is touched, \eg
petted or caressed); \textbf{show} (show something to the robot); \textbf{call}
(call the robot to come over); \textbf{talk} (all the other cases of direct
verbal interaction); \textbf{look} (when a child looks \emph{at the
experimenter} due to confusion caused by the robot; look is not coded when the
experimenter asks a question to the child);

@@

\subsubsection{Engagement}

@@

We have measured engagement by combining \emph{interaction} data with the
results of the semi-structured interviews.  Several of the aforementioned coded
actions can reflect engagement: \textit{explore, misuse, gesture, touch, show,}
and \textit{talk}. Also, \textit{look} at the experimenter can be considered as
engagement in the interaction: We assume that children look at the experimenter
when they are surprised and seek for help.  This behaviour reflects that they
want to make sense of the robot's behaviour. Further, we can take into account
how they refer to Ranger and describe the robot (as well as their experience) in
the interviews.  Specifically, we used the constructs \textit{ascribe intention,
ascribe cognitive abilities, ascribe emotional state}, and \textit{ascribe moral
standing} (Table~\ref{tab:domino-questions}) to assess how far they engaged with
the robot.

To account for the fact that anthropomorphism arises in an interaction, we bring
both children's perception of the robot (post-measurement) and their behaviour
toward it (in-the-moment measurement) together. We did so by building a
anthropomorphism index~\cite{fink2014dynamics}. We quantify the
index by attributing points for each anthropomorphic \emph{perception} of the
robot (max.  13 points) and for specific kinds of human-like \emph{behaviour}
toward the robot (max.  3 points). The index included the following aspects:\\

@@

\subsection{Misbehaviour Recognition and Interaction Engagement}

\paragraph{Misbehaviour Recognition}

@@

\paragraph{Engagement}
In terms of \textbf{engagement}, the novelty of the robot certainly plays a role
here. The findings do not directly address the issues
of long-term usage but concern short-term \textit{engagement}, which is a
pre-requisite for long-term usage.

The huge proportion of \textit{explore} actions (52~\% of all coded actions)
already suggests that children were generally engaged in the interaction, and
most of the time carefully observed what the robot did. When considering the
actions \textit{explore, gesture, look, misuse, show, talk}, and \textit{touch}
as \textbf{engagement actions}, 1699 of the 2354 actions reflected engagement
(72~\%). This indicates that overall children were very engaged in the
interaction with the robot. Furthermore, data suggests that the robot in the
\textit{mistake} and \textit{lost} condition was more engaging for children
(each 75~\% of the actions reflected engagement) than the robot in the
\textit{disobey} condition (66~\% reflected engagement). The statistical
analysis supports this: An ANOVA indicates that there was a significant effect
of robot behaviour on the actions \textit{explore} (F(2,23)=11.31, p<.001) and
\textit{look} (F(2,23)=4.6, p=.021). Post-hoc comparisons using the Tukey's test
indicate that the mean score for \textit{explore} in the \textit{disobey}
condition is significantly different from the score in the \textit{mistake} and
\textit{lost} condition. This suggests that children explored the disobeying
robot less\footnote{It is surprising that the disobeying robot was explored
less. One may expect that the disobeying robot might better attract
children's attention because it faces the searcher child and uses fairly
strong audio and light cues as compared to the other behaviours.}.

Overall, we found a significant difference between the average of engagement
actions carried out during the first 7 runs (correct robot behaviour) and during
the second 7 runs, when the robot behaved unexpectedly (F(1,36)=5.1, p=.03). In
all three conditions, children carried out more engagement actions with the
unexpectedly behaving robot. No interaction effect was found between the two
phases of interaction (expected / unexpected) and condition (F(2,36)=1.2,
p=.31). In general, this finding supports our first hypothesis: children show
more engagement toward a robot that behaves unexpectedly from time to time
compared to a robot that always behaves correctly.

@@

To obtain the anthropomorphism index for a pair, we first calculated the index
per child and then took the average of the two children in one group.  The group
indexes varied between 3.25 and 10.75 points with an average of 7.5 points
(SD~=~2.5), which is 47~\% of the maximum possible index of 16 points.
Intra-group variations were interesting: In 7 of the 13 groups, the
anthropomorphism indexes for both children were similar (difference less than
1.5 points). This agreement among children happened for both higher and lower
indexes. In 6 of the 13 groups, the anthropomorphism indexes varied in more than
2 points, which means that one of the children anthropomorphized the robot more
than the other one.

On average, Ranger was moderately anthropomorphized by the children. 8 of the 13
groups had an index of 8 or higher, evenly spread over the three conditions
(Table~\ref{tab:domino-anth-score}). However, the mean index of anthropomorphism
in the three conditions varied, with the \textit{mistake} and \textit{lost}
condition leading to a higher index than the \textit{disobey} condition. This
finding suggests that the disobeying robot was less anthropomorphized than the
other two robot behaviours, which speaks against our second hypothesis. We had
expected that the disobeying behaviour is perceived as an intentional action
which we assumed would lead to increased anthropomorphism. This was not the
case. The slight difference between the \textit{lost} and \textit{mistake} robot
was also expected in the opposite direction. It could be that the robot's
``helplessness'' led to this. This is also reflected in children's behaviour:
with the lost robot, children looked more often at the experimenter than in the
other condition, which suggests that they could not fully make sense of the
robot's behaviour, and the fact of not being able to understand (and hence
predict) a robot's behaviour is likely to increase
anthropomorphism.\footnote{One of the cognitive / psychological explanations for
anthropomorphism is that people want to make sense of something they do not
understand and then tend to anthropomorphize this something (human traits
are a good source of making attributions because this is what people
understand best -- themselves and other humans). For more details the reader may
refer to \cite{epley_seeing_2007}.}

\begin{table}[ht!]
    \centering
    \footnotesize
    \begin{tabular}{lccc}
        \toprule
        & M & SD & groups with index > 8 \\
        \midrule

        \textit{lost} & \textbf{8.31} & 0.59 & 3 of 4 \\ 
        \textit{disobey} & 6.5 & 3.68 & 2 of 5 \\
        \textit{mistake} & 7.94 & 1.74 & 3 of 4 \\ 
        \bottomrule
    \end{tabular}
    \caption{\textbf{Anthropomorphism index.} The maximum possible index was 16. The
    \textit{lost} robot elicits the highest index, which suggests that it is
    anthropomorphized more. Contrary to our hypothesis, data suggests that the
    \textit{disobeying} robot is anthropomorphized less but the \textit{lost} robot
    more.}

    \label{tab:domino-anth-score}       % Give a unique label
\end{table}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\columnwidth]{domino-correlation.pdf}

@@

Interestingly, data suggests a significant negative correlation of engagement
and anthropomorphism index. It appears that groups who interacted more with the
robot perceived it as less human-like. This raises an important question for the
human-robot interaction community: to what extent do anthropomorphic perceptions
impact the interaction experience? Our findings here go against the intuition.

>>>>

\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\subsection{Towards Sustained Engagement}

@@

    \item[Hypothesis 1:] Children show more engagement toward a robot that
        behaves unexpectedly from time to time compared to a robot that always
        behaves correctly.

    \item[Hypothesis 2:] Children perceive a robot that (tentatively) displays
        intention or cognitive abilities as more human-like than a robot that
        appears to have a system error, \ie the disobeying robot and the robot
        that makes a mistake will be more anthropomorphized than the robot that
        gets lost.

@@

\subsection{Experimental Setting}

\begin{figure}[ht!] 
    \centering 
    \includegraphics[width=0.8\columnwidth]{domino-setup.pdf} 
    \caption{\small \textbf{Experimental setting} One child is located in a
        tent, while the other is asked to sit on one of the three beanbags,
        behind each of which 3 domino tiles are distributed. A play mat with a
        river drawn on it is used as an imaginary barrier that only the robot is
        allowed to cross. The solid green arrows show the robot's path for the
        \textit{correct} behaviour. The blue arrow visualises a possible
        \textit{lost} path, where the Ranger stops and remains at a wrong spot.
        The yellow arrows reflect a possible \textit{mistake} path, where the
        robot goes wrong but then turns back and goes to the child. The red
        arrow visualises a possible \textit{disobey} path where the robot goes
        wrong, then turns toward the child but stays at a wrong position.}

@@

%We used a self-made domino consisting of 10 wooden tiles (10~x~20~x~1.5~cm) with
%pictures of cartoon farm animals (taken from a commercially available domino
%game manufactured by Djeco and adapted to the age of the children).

@@

%In 11 of the pairs, children were friends who knew each other
%from kindergarten, nursery school or because they lived in the same
%neighbourhood. 2 of the pairs were composed of brother and sister. One parent
%would generally attend, sit on a chair behind the children.

\subsection{Course of the Study}

The game was divided in a total of 14 runs that correspond each to the delivery
and assembling of one domino tile. At each run, the robot exhibits one out of
four possible behaviours: \emph{correct}, \emph{lost} \emph{disobey} or
\emph{mistake}.  The game starts with one domino tile in front of the tent,
where the receiver child stays and assembles the domino chain. The receiver
child asks the searcher child for a specific tile, \eg a tile with a donkey, the
searcher child searches for the respective tile and sits down on the next
beanbag. When called by the searcher (\textit{``Robot, come here!''}), the robot
starts moving, crosses the river carpet, and comes over to the searcher on the
beanbag. The searcher child puts the domino tile into the robotic box, and the
robot then goes back to the receiver child in the tent which takes the tile and
assembles it. The \emph{run} is over, and a new \emph{run} starts when the
receiver asks the searcher for the next domino tile.

The first 5 runs (\emph{1.1} to \emph{1.5}) were used to set
the baseline and the robot always behaved correctly. The children then switched
the roles receiver/searcher and in the 9 remaining runs (\emph{2.1} to
\emph{2.9}), the robot showed one of the misbehaviours (\emph{lost},
\emph{disobey} or \emph{mistake}) at the $3^{rd}$ and $4^{th}$ run as well as at
the $7^{th}$ and $8^{th}$ run (see Figure~\ref{fig:domino-time-active}).
%The
%study is built as a between-subject study, and the type of misbehaviour was
%therefore always the same for a given group.

@@

%The \emph{correct} robot behaviour (baseline behaviour) consists in the
%following states:
%
%\begin{itemize}
%
%    \item \emph{Domino tile put in robot:} Ranger makes a ``rewarding'' sound
%        and shows a green light pattern,
%
%    \item \emph{Domino tile removed from robot:} Ranger makes an ``emptying''
%        sound and shows a green light pattern,
%
%    \item \emph{Robot is called by one of the children:} When one of the
%    children called the robot saying something like \textit{``Robot come
%    here!''}, the robot starts moving toward the child (Ranger does not react to
%    any other verbal commands).
%
%    \item \emph{Robot reaches one of the children:} When in front of one of the
%    children who should either put or remove a domino tile, Ranger stops and
%    shows a pulsating yellow light pattern. If no reaction, Ranger also makes a
%    wiggle-like move.
%
%\end{itemize}
%
During the misbehaving runs, the robot's behaviour is manipulated in three
possible ways, represented on Figure~\ref{fig:domino-setup}.
In the \textbf{lost} condition, goes to a wrong position, and remains here,
behaving (yellow light pattern) as if it were correctly in front of the child.
In the \textbf{disobey} condition, the robot stops mid-way, displays a red
pattern and produces a repeated ``annoyed'' sound. It finally moves toward a
wrong position and remains there, facing the child. In the \textbf{mistake}
condition, the robot starts like for the \emph{lost} behaviour, but after a few
seconds, turns back, blushes and finally reach the correct position, in front of
the child.

%\begin{itemize}	
%
%    \item \textbf{Lost:} After being called, Ranger goes until it is on the
%    carpet. There, it stops, turns, and goes wrong (see blue path in
%    Figure~\ref{fig:domino-setup}). Once at the wrong position, Ranger waits
%    with its ``face'' turned away from the child, and it blinks in yellow light,
%    as it would only do when in front of a child. Ranger remains waiting at the wrong
%    position until the experimenter tells the child to go over to the robot to
%    put the domino tile. The \textit{lost} behaviour is \textit{human-repaired},
%    as it needs human-intervention.
%
%    \item \textbf{Disobey:} After being called, Ranger goes until it is on the
%    carpet. It then stops, makes red
%    light all over its surface and produces a repeated ``disturbance'' sound. It
%    turns, and goes to a wrong position (see red path in
%    Figure~\ref{fig:domino-setup}). Still blinking in red, it turns its ``face''
%    toward the searcher child. In addition to the red blinking, Ranger
%    makes a slow wiggle-like move, and remains waiting at the wrong position
%    until the experimenter tells the child to go over to the robot to put the
%    domino tile. The \textit{disobey} behaviour is also \textit{human-repaired}.
%
%    \item \textbf{Mistake:} The searcher child calls Ranger. The robot goes until
%    it is on the carpet, stops, turns, and goes wrong (see yellow path in
%    Figure~\ref{fig:domino-setup}). Then, Ranger waits ($\sim$2~sec), turns its
%    ``face'' toward the searcher child, and ``blushes'' red around its ``cheeks''
%    (as if it recognises its wrong position) and finally goes correctly over to
%    the searcher child. The \textit{mistake} behaviour is \textit{robot-repaired},
%    as no human-intervention is needed.
%
%\end{itemize}

Both the \textit{lost} and \emph{disobey} behaviours are
\textit{human-repaired}, while the \emph{mistake} condition is
\emph{robot-repaired}. In the human-repaired conditions, the experimenter
instructs the searcher child (after ~10 sec) to bring him/herself the domino
tile to the robot.

@@

\begin{figure*}[ht!] 
    \centering 
    \includegraphics[width=0.8\linewidth]{domino-time-active.pdf} 
    \caption{\small \textbf{Number and type of actions for each run} (n=480,
        spontaneous actions, excluding \emph{explore}). Generally, the number of
        actions does not decrease over time (from run 1.1 to run 2.9).  The
        first 7 runs correspond to the \textit{expected phase}, the second 7
        runs correspond to the \textit{unexpected phase}. Especially during run
        2.3, the first time when the robot showed an unexpected behaviour,
        children tended to \textit{look} more at the experimenter. During the
        unexpected phase, also \textit{talk} and \textit{gesture} seem to be
        increased.}

@@

One coder annotated children's behaviour in the video records, and coded 10 different
actions (the coding scheme has been inspired from~\cite{fink2014which}):
\textbf{explore} (actively try to find out what the robot is doing, \eg by
looking under the box; attentively watch or observe the robot; experiment with
the robot to figure out how it works); \textbf{misuse} (kick the robot, poke it
in its ``eye'', try to climb on or inside the box, drive/push the robot around,
stop the robot's wheels with a foot); \textbf{put} (a domino tile is put inside
the box); \textbf{remove} (a domino tile is removed from the box);
\textbf{gesture} (gestures are used to communicate/interact with the robot, \eg
pointing gestures, waving at the robot); \textbf{touch} (the box is touched, \eg
petted or caressed); \textbf{show} (show something to the robot); \textbf{call}
(call the robot to come over); \textbf{talk} (all the other cases of direct
verbal interaction); \textbf{look} (when a child looks \emph{at the
experimenter} due to confusion caused by the robot; look is not coded when the
experimenter asks a question to the child);

@@

\subsubsection{Anthropomorphism Index}

@@

%We have measured engagement by combining \emph{interaction} data with the
%results of the semi-structured interviews.  Several of the aforementioned coded
%actions can reflect engagement: \textit{explore, misuse, gesture, touch, show,}
%and \textit{talk}. Also, \textit{look} at the experimenter can be considered as
%engagement in the interaction: We assume that children look at the experimenter
%when they are surprised and seek for help.  This behaviour reflects that they
%want to make sense of the robot's behaviour. Further, we can take into account
%how they refer to Ranger and describe the robot (as well as their experience) in
%the interviews.  Specifically, we used the constructs \textit{ascribe intention,
%ascribe cognitive abilities, ascribe emotional state}, and \textit{ascribe moral
%standing} (Table~\ref{tab:domino-questions}) to assess how far they engaged with
%the robot.
%
To account for the fact that anthropomorphism arises in an interaction, we bring
both children's perception of the robot (post-measurement) and their behaviour
toward it (in-the-moment measurement) together. We did so by building a
anthropomorphism index~\cite{fink2014dynamics}. We quantify the
index by attributing points for each anthropomorphic \emph{perception} of the
robot and for specific kinds of human-like \emph{behaviour}
toward the robot. The index included the following aspects:\\

@@

\subsection{Misbehaviour Recognition, Engagement}

%\paragraph{Misbehaviour Recognition}

@@

%\paragraph{Engagement}
In terms of \textbf{engagement}, the novelty of the robot certainly plays a role
here. The findings do not directly address the issues
of long-term usage but concern short-term \textit{engagement}, which is a
pre-requisite for long-term usage.

The huge proportion of \textit{explore} actions (52~\% of all coded actions)
already suggests that children were generally engaged in the interaction, and
most of the time carefully observed what the robot did. When considering the
actions \textit{explore, gesture, look, misuse, show, talk}, and \textit{touch}
as \textbf{engagement actions}, 1699 of the 2354 actions reflected engagement
(72~\%). This indicates that overall children were very engaged in the
interaction with the robot.
%Furthermore, data suggests that the robot in the
%\textit{mistake} and \textit{lost} condition was more engaging for children
%(each 75~\% of the actions reflected engagement) than the robot in the
%\textit{disobey} condition (66~\% reflected engagement). The statistical
%analysis supports this: An ANOVA indicates that there was a significant effect
%of robot behaviour on the actions \textit{explore} (F(2,23)=11.31, p<.001) and
%\textit{look} (F(2,23)=4.6, p=.021). Post-hoc comparisons using the Tukey's test
%indicate that the mean score for \textit{explore} in the \textit{disobey}
%condition is significantly different from the score in the \textit{mistake} and
%\textit{lost} condition. This suggests that children explored the disobeying
%robot less\footnote{It is surprising that the disobeying robot was explored
%less. One may expect that the disobeying robot might better attract
%children's attention because it faces the searcher child and uses fairly
%strong audio and light cues as compared to the other behaviours.}.

We found a significant difference between the average of engagement
actions carried out during the first 7 runs (correct robot behaviour) and during
the second 7 runs, when the robot behaved unexpectedly (F(1,36)=5.1, p=.03). In
all three conditions, children carried out more engagement actions with the
unexpectedly behaving robot. No interaction effect was found between the two
phases of interaction (expected / unexpected) and condition (F(2,36)=1.2,
p=.31). In general, this finding supports our first hypothesis: children show
more engagement toward a robot that behaves unexpectedly from time to time
compared to a robot that always behaves correctly.

@@

%To obtain the anthropomorphism index for a pair, we first calculated the index
%per child and then took the average of the two children in one group.  The group
%indexes varied between 3.25 and 10.75 points with an average of 7.5 points
%(SD~=~2.5), which is 47~\% of the maximum possible index of 16 points.
%Intra-group variations were interesting: In 7 of the 13 groups, the
%anthropomorphism indexes for both children were similar (difference less than
%1.5 points). This agreement among children happened for both higher and lower
%indexes. In 6 of the 13 groups, the anthropomorphism indexes varied in more than
%2 points, which means that one of the children anthropomorphized the robot more
%than the other one.

On average, Ranger was moderately anthropomorphized by the children. 8 of the 13
groups had an index of 8 or higher, evenly spread over the three conditions.
However, the mean index of anthropomorphism in the three conditions varied, with
the \textit{mistake} and \textit{lost} condition leading to a higher index than
the \textit{disobey} condition. This finding suggests that the disobeying robot
was less anthropomorphized than the other two robot behaviours, which speaks
against our second hypothesis. We had expected that the disobeying behaviour is
perceived as an intentional action which we assumed would lead to increased
anthropomorphism. This was not the case. The slight difference between the
\textit{lost} and \textit{mistake} robot was also expected in the opposite
direction. It could be that the robot's ``helplessness'' led to this. This is
also reflected in children's behaviour: with the lost robot, children looked
more often at the experimenter than in the other condition, which suggests that
they could not fully make sense of the robot's behaviour, and the fact of not
being able to understand (and hence predict) a robot's behaviour is likely to
increase anthropomorphism.\footnote{One of the cognitive / psychological
explanations for anthropomorphism is that people want to make sense of
something they do not understand and then tend to anthropomorphize this
something (human traits are a good source of making attributions because
this is what people understand best -- themselves and other humans). For
more details the reader may refer to~\cite{epley_seeing_2007}.}
%
%\begin{table}[ht!] \centering \footnotesize \begin{tabular}{lccc} \toprule & M
%& SD & groups with index > 8 \\ \midrule
%
%        \textit{lost} & \textbf{8.31} & 0.59 & 3 of 4 \\ \textit{disobey} & 6.5
%        & 3.68 & 2 of 5 \\ \textit{mistake} & 7.94 & 1.74 & 3 of 4 \\
%        \bottomrule \end{tabular} \caption{\small \textbf{Anthropomorphism
%        index.} The maximum possible index was 16. The \textit{lost} robot
%        elicits the highest index, which suggests that it is anthropomorphized
%        more. Contrary to our hypothesis, data suggests that the
%        \textit{disobeying} robot is anthropomorphized less but the
%        \textit{lost} robot more.}
%
%    \label{tab:domino-anth-score}       % Give a unique label
%\end{table}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.6\columnwidth]{domino-correlation.pdf}

@@

Interestingly, data suggests that anthropomorphic perception does not
automatically elicit  engagement, on the contrary. It appears that groups who
interacted more with the robot perceived it as less human-like. This raises an
important question for the human-robot interaction community: to what extent do
anthropomorphic perceptions impact the interaction experience? Our findings here
go against the intuition.
